---
title: "Homework 5"
author: "Jae Hoon Cho"
date: "October 13, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1 
Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with N = 1000 and 10000.

```{r}
dice_game <- function () {
  result <- sample (1:6, 4, replace=T)
  ifelse (result[1]==6|result[2]==6|result[3]==6|result[4]==6, return(1), return(0))} 

dice_prob <- function(B) {
sum(replicate (B, dice_game()))/B}

dice_prob(1000)
dice_prob(10000)
```

# Question 2
Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element.
Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.

```{r}
x=c(3,4,5,6,7,3)


findMin <- function(x) {for (i in 1:length(x)){
  if(sum(x[i]<=x)!=length(x)){
    next
  }
  print (paste("minimum number is",x[i]))
  print (paste("its sequence",i))
}}

findMin(x)
```